---
author: "Carl Boettiger"
institute: "UC Berkeley"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: ["default", "solarized-light.css"]
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: "solarized-light"
      highlightLines: true
      countIncrementalSlides: false
      slideNumberFormat: "%current%"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(#dev.args=list(bg="transparent"), 
                      echo = FALSE, 
                      message=FALSE, 
                      warning=FALSE,
                      fig.width=11, 
                      fig.height=6.5, 
                      cache = TRUE)

library(tidyverse)
library(ggthemes)
library(magick)
theme_set(theme_solarized(base_size=22))
scale_colour_discrete <- function(...) scale_colour_solarized()
scale_fill_discrete <- function(...) scale_fill_solarized()
pal <- solarized_pal()(8)

txtcolor <- "#586e75"


library(patchwork)

ggimage <- function(path, transparent = FALSE){
  img <- magick::image_read(path)
  if(transparent)  img <- magick::image_transparent(img, "white")
  ggplot2::ggplot() + 
  ggplot2::annotation_raster(img, 
                    xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf)  +   theme(axis.line = element_blank(), 
  panel.background = element_blank())
}

```

layout: true
background-color: #fdf6e3
class: center, top

---

# From Oceans to Fields: Socio-ecological Decision Making for the 21st Century


<div class="my-footer">

<a href="https://carlboettiger.info"> `r icon::fa("user")` Carl Boettiger</a> | 
<a href="https://berkeley.edu"> `r icon::fa("briefcase")` UC Berkeley</a> | 
<a href="https://twitter.com/cboettig"> `r icon::fa("twitter")` @cboettig</a>

</div>

---

# First Slide

.pull-left[

- bulleted list
- the bullets are invisible
- that's nicer for centered text

]
.pull-right[

```{r fig.width=6, fig.height=4}
ggplot(mtcars, aes(cyl, mpg, fill=as.factor(cyl))) +
  geom_bar(stat="identity", show.legend = FALSE) + 
  ggtitle("Not mtcars again!")
```
]


---

# Reproducibility

---

# Acknowledgements

.pull-left[

```{r fig.width=6, fig.height=6}
(ggimage("../image-library/people/milad.png") +
ggimage("../image-library/people/millie.png")) / 
(ggimage("../image-library/people/serge.png") +
ggimage("../image-library/people/claire-kremen.jpg", TRUE))

```

]
.pull-right[

```{r fig.width=6, fig.height=6}
ggimage("../image-library/people/dfs-cnh.jpg") /
  (ggimage("../image-library/sponsors/nsf.png")  +     
    (ggimage("../image-library/sponsors/jetstream-logo.svg", TRUE) /     
     ggimage("../image-library/sponsors/berkeley.png")  
    ) +  plot_layout(ncol = 2, widths = c(1, 2))
  ) + plot_layout(ncol = 1, heights = c(2, 1))

```

```{r}
ggimage("../image-library/sponsors/jetstream-logo.svg", TRUE)
```

]